---
title: "Bucketed regressions"
author: "neha"
date: "2023-09-05"
output: html_document
---


```{r, echo=FALSE, results='hide'}

library(ggplot2)
library(survey)
library(dplyr)
library(survey)
library(haven)
library(tidyr)
library(stringr)
library(sf)
library(gridExtra)
library(labelled)



setwd('C:/Users/neha.verghese/Downloads/IAKR7EDT')

geo<- st_read("C:/Users/neha.verghese/Downloads/IAKR7EDT/NFHS_Shp_Correct.shp")

kr_geo <- geo %>% filter(OTHREGCO== 29)

kr<- readRDS('kr.rds')
kr <- kr %>% mutate(stunting= ifelse(hw70< -200, 1, 0))

kr<- kr %>% filter(hw70<9989) %>% filter(v024==29) %>%
  filter(hw1<60)%>%
  mutate(stunting= ifelse(hw70< -200, 1, 0)) %>% 
  mutate(wt=v005/1e6)%>%
  filter(!is.na(stunting))%>%
  mutate(caste=as.factor(s116))%>%
  mutate(gender=as.factor(b4))%>%
  mutate(wealth=as.factor(v190))%>%
  mutate(ur=as.factor(v025)) %>%
  mutate(religion=as.factor(v130))%>%
  mutate(states=as.factor(v024)) 



#MATERNAL HEALTH

kr <- kr %>% mutate(visited_awc= ifelse(s562==2 | s562==1, 1, 0))
kr <- kr %>% mutate(no_ed= ifelse(v106==0, 1, 0))%>% 
  mutate(low_bmi= ifelse(v445>=1200 & v445<=1699, 1, 0)) %>% mutate(ba= (v447a*12)-b19) %>% 
  mutate(ba18= ifelse(ba<=216, 1, 0)) %>%  mutate(od= ifelse(v116==31, 1, 0)) %>% 
  mutate(anc= as.factor(s414)) %>% mutate(iron_sup= ifelse(m45 == 1, 1, 0)) %>%
  mutate(mass_media= ifelse(v157 %in% c(2, 3) & v158 %in% c(2,3) & v159 %in% c(2,3), 1, 0 ))

#HOUSEHOLD ENIVORNMENT

kr<- kr %>% mutate(fuel_type= ifelse(v161==1 | v161 == 2 | v161 == 3 | v161 == 4, 
                                  'cleanfuel',
                                  ifelse(v161==95 | v161== 96 | v161==97, 'other', 'uncleanfuel'))) %>% 
  mutate(source_drinking= ifelse(v113== 10 | v113== 11 | v113==12 | v113==14 |
                                   v113== 13 | v113== 20 | v113==21 | v113==30 | v113==41 |
                                   v113==51 | v113==71, 'improvedsource', 
                                 ifelse(v113==96 | v113==97, 'other','unimprovedsource'  ))) %>%
  mutate(toilet_facility= ifelse(v116==10 | v116 == 11 | v116== 12 | v116 == 13 | v116 == 14 |
                                   v116== 15,'facility available',
                                 ifelse(v116==96|v116==97,'other', 'facility not available')))

# CHILD HEALTH
kr <- kr %>% mutate(eb= ifelse(m34 %in% c(199,201, 299, NA), 0, 1)) %>% 
          mutate(exc_b= v404 %in% c(0, NA) & b19 > 6 & b9 %in% c(1, 2, 3, 4, NA) & v409 %in% c(1, 8, NA) & v410
                 %in% c(1, 8, NA) & 
                         v411 %in% c(1, 8, NA) & v411a %in% c(1, 8, NA) & 
                        v412a%in% c(1, 8, NA)  &
                        v412c %in% c(1, 8, NA) & v413 %in% c(1, 8, NA) & v414a %in% c(1, 8, NA) &
                        v414e%in% c(1, 8, NA) & 
                        v414f %in% c(1, 8, NA) & v414g %in% c(1, 8, NA)  &
                      v414i %in% c(1, 8, NA) & v414j %in% c(1, 8, NA) & v414k%in% c(1, 8, NA) & 
                        v414l %in% c(1, 8, NA) & v414m %in% c(1, 8, NA) & v414n%in% c(1, 8, NA) &  
                        v414o %in% c(1, 8, NA) & v414p%in% c(1, 8, NA)  & 
                      v414s %in% c(1, 8, NA) & v414t %in% c(1, 8, NA) & 
                       v414v %in% c(1, 8, NA)  &
                      m39a %in% c(1, 8, NA), 0, 1) %>% mutate(vitA=ifelse(h34 %in% c(0, NA, 8), 0, 1)) %>% 
  mutate(immune= ifelse(h3 %in% c(0, 8, NA) & h4 %in% c(0, 8, NA) & h5 %in% c(0, 8, NA) & h6 %in% c(0, 8, NA)
                        & h7 %in% c(0, 8, NA) & h8 %in% c(0, 8, NA) & h9 %in% c(0, 8, NA) & h9a %in% c(0, 8, NA), 0, 1 )) %>%
  mutate(oral_rehyd= ifelse(h11 %in% c(0, 8, NA) & h13 %in% c(0, 8, NA) , 0,  1 )) %>%
  mutate(postnatal = ifelse(m70 %in% c(0, 8, NA), 0, 1)) %>% mutate(diarrhea = ifelse(h11==1 | h11==2, 1, 0)) %>%
  mutate(inst_delivery= ifelse(m15 %in% c(20, 21, 22, 23, 24,25, 26, 27) & m15 %in% c(30, 31, 32, 33), 1, 0 )) %>%
  mutate(birth_size= ifelse(m18== 4 | m18== 5, 1, 0)) %>% mutate(low_birth_wt= ifelse(m19<=2.5, 1, 0)) %>%
  mutate(zinc_d= ifelse(h11 %in% c(0,8) & h15e %in% c(0, 8, NA), 0, 1 )) %>% mutate(ifelse(bord != 1, 1, 0)) %>% mutate(sev_anemia= ifelse(hw57 %in% c(2, 3, 4, NA), 0, 1))

kr %>% select(s116, b4, v025, s562, v106, v445, v447a, v116, anc, m45, v157, v161, v113, v116, 
              m34,  exc_b, v411, v412a, v412c,v411a, v413, v414a, v414e, v414f, v414i, v414o, v414s, v414v, m39a, v414t, h34, h3, h5, h4, h6 ,h7, h8, h11, m70, m15, m18, m19, h11, bord, hw57, h9a, h13, h11, h15e  ) 
  
#cultural norms 


#select 

kr<-  kr %>%  mutate(od= ifelse(v116==30 | v116 == 31, 1, 0)) %>% mutate(districts= as.factor(sdist))

kr_a <- kr%>%  select(v021, v025, wt, sdist, v005, v008, b3, v024, stunting, caste, gender, wealth, religion, ur, states, districts, fuel_type, source_drinking, s116, v130,
             toilet_facility, eb, exc_b, vitA, immune, oral_rehyd, postnatal, diarrhea, inst_delivery, 
             birth_size, low_birth_wt, zinc_d, bord, sev_anemia, son_pref, od, districts, no_ed, low_bmi, ba18, anc, iron_sup, mass_media )

library(forcats)

kr_a <- kr_a %>% mutate(caste_religion= paste(as_factor(s116), as_factor(v130), sep = " "), caste_religion = fct_lump_prop(caste_religion, prop=0.05, other_level = "Other"))
kr_a$caste_religion

k_districts<- c("Belgaum", "Bagalkot", "Bijapur", "Bidar", "Raichur", "Koppal", "Gadag", 
                "Dharwad", "Uttara Kannada", "Haveri", "Bellary", "Chitradurga", "Davanegere","Shimoga", 
                "Udupi", "Chikmagalur", "Tumkur", "Bangalore", "Mandya", "Hassan", "
                Dakshina Kannada", "Kodagu", "Mysore", "Chamarajanagar", "Gulbarga",
                "Yadgir", "Kolar", "Chikkaballapura", "Bangalore Rural")

syd<- svydesign(id=kr$v021, strata = kr$v025, weights=kr$wt, data=kr)

svyglm(stunting ~ od + gender + ur + adminzone, syd, family = binomial(link = "logit"))

```

note: 

- The regression model interprets NA values as 0 (or respondent was not exposed treatment variable)- which may not be entirely accurate. 

model 1 : controlling for socio economic and demographic features

```{r}

modeldistricts<- svyglm(stunting ~ relevel(districts, ref='584') + gender + wealth + caste_religion + ur, 
                syd, family=binomial(link="logit"))

ci<- confint(modeldistricts, level=0.95)

ci_l <- ci[, 1] %>% exp()
ci_u<-  ci[, 2] %>% exp()

r_0<- data.frame(summary(modeldistricts)$coefficient)

r_0<- tibble::rownames_to_column(r_0, "coefficients")

r_0 <- r_0 %>% mutate(ci_l = ci_l) %>% mutate(ci_u = ci_u)

r_0 <- r_0 %>% filter(str_length(coefficients) == 34 ) 

r_0$coefficients <- substr(r_0$coefficients, 32, 34)

r_0<- r_0[-30:-31, ]

r_0 <- r_0 %>% mutate(odds_ratio = exp(Estimate)) 
r_0 <- r_0 %>% mutate(districts = k_districts)

r0_geo<- merge(r_0, kr_geo, by.x = "coefficients", by.y = "REGCODE")

r0_geo<- r0_geo %>% mutate(odds_ratio = exp(Estimate))

```

Bar graphs

```{r}
ggplot(r_0) + geom_bar(aes(x= reorder(districts, odds_ratio), y=odds_ratio), fill="#009900", stat="identity") + 
  geom_errorbar(aes(x=reorder(districts, odds_ratio), ymin=ci_l, ymax=ci_u)) + xlab("districts") + ylab("odds ratio")+ 
 labs(title= "stunting odds ratios across districts", subtitle="controlling for socioeconomic factors") +
  coord_flip() 
```

```{r, echo=FALSE}

r0_g1<- ggplot(r0_geo) + geom_sf(aes(geometry=geometry, fill=odds_ratio), stat="sf")+ scale_fill_gradient2(low = "#FF9999",
  mid = "white",
  high = "darkred",
  midpoint = 1,
  space = "Lab"
  ) + labs(fill="odds ratio")  + labs(fill="odds ratio") + labs(title="stunting odds ratio", subtitle = "controlling for socioeconomic and demographic factors")

r0_g2<- ggplot(r0_geo) + geom_sf(aes(geometry=geometry, fill=Pr...t..), stat="sf")+ scale_fill_gradient2(low = "darkred" ,
  high ="#FFFF99", mid="white", midpoint= 0.05,
  ) + labs(fill="odds ratio")  + labs(fill="p-value") + labs(title="stunting p-value", subtitle = "controlling for socioeconomic and demographic factors")

r0_g2

grid.arrange(r0_g1,r0_g2 , nrow=1)

```

model 2 : 

Controlling for child health bucket variables :

early initiation of breastfeeding, exclusive breastfeeding, vitamin A, immunization, oral re-hydration, postnatal care, whether the child had diarrhea two weeks preceding the survey, institutional delivery, birth size, low birth weight, whether the child took zinc if and when they had diarrhea, birth order and anemia level

WHO recommendation for exclusive breastfeeding is up to 6 months- so creating a dichotomous variable for children who are exclusively breastfed and are below the age of 6 months 
problem with measuring exclusive breastfeeding : you'll only be able to measure stunting for below 6 months child
but there is a number of 6 month old stunted children - so we let it be
exclusive breastfeeding would be better studied in panel data regressions 

note: 

- adequate diet has been skipped : need proper research papers that actually provide info what kind of diet for which age groups 
- h34- vitamin A in the last 3 months taken by the child 

- immunization- received all 3 doses of BCG, POLIO, DPT and 2 doses of Measles (+ Polio 0)
early breastfeeding is initiation within one day 

``` {r}

modeldistricts<- svyglm(stunting ~ relevel(districts, ref='584') + gender + wealth + caste_religion + ur + 
                           eb + exc_b + vitA +  immune + oral_rehyd + postnatal + diarrhea +  inst_delivery + 
             birth_size + low_birth_wt + zinc_d + bord + sev_anemia, syd, family=binomial(link="logit"))

ci<- confint(modeldistricts, level=0.95)

ci_l <- ci[, 1] %>% exp()
ci_u<-  ci[, 2] %>% exp()

r<- data.frame(summary(modeldistricts)$coefficient)

r<- tibble::rownames_to_column(r, "coefficients")

r <- r %>% mutate(ci_l = ci_l) %>% mutate(ci_u= ci_u)

r <- r%>% filter(str_length(coefficients) == 34 ) 

r$coefficients <- substr(r$coefficients, 32, 34)

r<- r[-30:-31, ]

r <- r %>% mutate(odds_ratio = exp(Estimate)) %>% mutate(districts= k_districts)

r

```

bar charts

```{r}

ggplot(r) + geom_bar(aes(x= reorder(districts, odds_ratio), y=odds_ratio), fill="#009900", stat="identity") + 
  geom_errorbar(aes(x=reorder(districts, odds_ratio), ymin=ci_l, ymax=ci_u)) + xlab("districts") + ylab("odds ratio")+ 
 labs(title= "stunting odds ratios across districts", subtitle="controlling for socioeconomic factors") +
  coord_flip() 

```


```{r, echo=FALSE}

r_geo<- merge(r, kr_geo, by.x = "coefficients", by.y = "REGCODE")

r_g1<- ggplot(r_geo) + geom_sf(aes(geometry=geometry, fill=odds_ratio), stat="sf")+ scale_fill_gradient2(low = "#FF9999",
  mid = "white",
  high = "darkred",
  midpoint = 1,
  space = "Lab",
  guide = "colourbar",
  aesthetics = "fill" ) + labs(fill="odds ratio")  + labs(title="stunting odds ratio", subtitle="controlling for child health measures")
                                                                                                
r_g2<- ggplot(r_geo) + geom_sf(aes(geometry=geometry, fill=Pr...t..), stat="sf")+ scale_fill_gradient2(low = "darkred" ,
  high ="blue", mid="white", midpoint= 0.05,
  ) + labs(fill="odds ratio")  + labs(fill="p-value") + labs(title="stunting p-value", subtitle = "child health measures")

grid.arrange(r_g1,r_g2 , nrow=1)


```

model 3

controlling for maternal health bucket variables : 
antenatal care, bmi, iron supplements during pregnancy. 

```{r}

modeldistricts2<- svyglm(stunting ~ relevel(districts, ref='584') + gender + wealth + caste_religion + ur + 
                         anc+ low_bmi+ iron_sup, syd, family=binomial(link="logit"))

ci <- confint(modeldistricts2)

ci_l<- ci[,1] %>% exp()
ci_u<- ci[,2] %>% exp()


r2<- data.frame(summary(modeldistricts2)$coefficient)

r2<- tibble::rownames_to_column(r2, "coefficients")

r2<- r2 %>% mutate(ci_l= ci_l)%>% mutate(ci_u= ci_u)

r2 <- r2%>% filter(str_length(coefficients) == 34 ) 

r2$coefficients <- substr(r2$coefficients, 32, 34)

r2<- r2[-30:-31,  ]

r2 <- r2 %>% mutate(odds_ratio = exp(Estimate)) %>% mutate(districts = k_districts)

r2

```

bar charts

```{r}

ggplot(r2) + geom_bar(aes(x= reorder(districts, odds_ratio), y=odds_ratio), fill="#009900", stat="identity") + 
  geom_errorbar(aes(x=reorder(districts, odds_ratio), ymin=ci_l, ymax=ci_u)) + xlab("districts") + ylab("odds ratio")+ 
 labs(title= "stunting odds ratios across districts", subtitle="controlling for socioeconomic factors") +
  coord_flip() 

```

```{r, echo=FALSE}

r2_geo<- merge(r2, geo, by.x="coefficients", by.y="REGCODE")

r2_g1<- ggplot(r2_geo) + geom_sf(aes(geometry=geometry, fill=Estimate), stat="sf")+ scale_fill_gradient2(low = "#FF9999",
  mid = "white",
  high = "darkred",
  midpoint = 1,
  space = "Lab"
  ) + labs(fill="odds ratio")  + labs(title="stunting odds ratio", subtitle="controlling for maternal health measures")

r2_g2<- ggplot(r2_geo) + geom_sf(aes(geometry=geometry, fill=Pr...t..), stat="sf")+ scale_fill_gradient2(low = "darkred" ,
  high ="#FFFF99", mid="white", midpoint= 0.05,
  ) + labs(fill="odds ratio")  + labs(fill="p-value")  + labs(title="stunting p-value", subtitle="controlling for maternal health measures")


```

model 4 :

controlling for household environment variables 

```{r}

modeldistricts3<- svyglm(stunting ~ relevel(districts, ref='584') + gender + wealth + caste_religion + ur +
                         fuel_type+source_drinking+od, syd,  family=binomial(link="logit"))

ci<- confint(modeldistricts3, level=0.95) 

ci_l<- ci[,1] %>% exp()

ci_u<- ci[,2] %>% exp()

r3<- data.frame(summary(modeldistricts3)$coefficient)
r3<- tibble::rownames_to_column(r3, "coefficients")

r3<- r3 %>% mutate(ci_l= ci_l) %>% mutate(ci_u= ci_u)

r3 <- r3 %>% filter(str_length(coefficients) == 34 ) 
r3$coefficients <- substr(r3$coefficients, 32, 34)

r3<- r3[-30:-31, ]

r3 <- r3 %>% mutate(odds_ratio = exp(Estimate)) %>%
  mutate(districts= k_districts)

```

bar charts

```{r}

ggplot(r3) + geom_bar(aes(x= reorder(districts, odds_ratio), y=odds_ratio), fill="#009900", stat="identity") + 
  geom_errorbar(aes(x=reorder(districts, odds_ratio) , ymin=ci_l, ymax=ci_u)) + xlab("districts") + ylab("odds ratio")+ 
 labs(title= "stunting odds ratios across districts", subtitle="controlling for socioeconomic factors") +
  coord_flip()

```

```{r, echo=FALSE}

r3_geo <- merge(r3, geo, by.x="coefficients", by.y="REGCODE")

r3_g1<- ggplot(r3_geo) + geom_sf(aes(geometry=geometry, fill=Estimate), stat="sf")+ scale_fill_gradient2(low ="#FF9999",
  mid = "white",
  high = "darkred",
  midpoint = 1,
  space = "Lab"
  ) + labs(fill="odds ratio")  + labs(fill="odds ratio")  + labs(title="stunting odds ratio", subtitle="controlling for household environment measures")

r3_g2<- ggplot(r3_geo) + geom_sf(aes(geometry=geometry, fill=Pr...t..), stat="sf")+ scale_fill_gradient2(low = "darkred" ,
  high ="#FFFF99", mid="white", midpoint= 0.05,
  ) + labs(fill="p-value")  + labs(title="stunting p-value", subtitle="controlling for household environment measures")


grid.arrange(r3_g1,r3_g2 , nrow=1)

```

model 5 :

controlling for maternal autonomy variables: 
whether the mother gave birth before the age of 18, mother's educational attainment, mass media exposure(TV, radio and newspaper)

```{r}
modeldistricts4<- svyglm(stunting ~ relevel(districts, ref='584') + gender + wealth + caste_religion + ur + 
                         ba18 + no_ed + mass_media, syd,  family=binomial(link="logit"))

ci<- confint(modeldistricts4, level= 0.95)

ci_l<- ci[, 1] %>% exp()
ci_u<- ci[, 2] %>% exp()

r4<- data.frame(summary(modeldistricts4)$coefficient)
r4<- tibble::rownames_to_column(r4, "coefficients")

r4 <- r4 %>% mutate(ci_l = ci_l) %>% mutate(ci_u = ci_u)

r4 <- r4%>% filter(str_length(coefficients) == 34 ) 
r4$coefficients <- substr(r4$coefficients, 32, 34)

r4<- r4[-30:-31, ]

r4 <- r4 %>% mutate(odds_ratio = exp(Estimate)) %>% mutate(districts= k_districts)

r4

```

bar chart 

```{r}

ggplot(r4) + geom_bar(aes(x= reorder(districts, odds_ratio), y=odds_ratio), fill="#009900", stat="identity") + 
  geom_errorbar(aes(x=reorder(districts, odds_ratio) , ymin=ci_l, ymax=ci_u)) + xlab("districts") + ylab("odds ratio")+ 
 labs(title= "stunting odds ratios across districts", subtitle="controlling for socioeconomic factors") +
  coord_flip()

```

```{r, echo=FALSE}

r4_geo<- merge(r4, geo, by.x="coefficients", by.y="REGCODE")

r4_g1 <- ggplot(r4_geo) + geom_sf(aes(geometry=geometry, fill=Estimate), stat="sf")+ scale_fill_gradient2(low = "#FF9999",
  mid = "white",
  high = "darkred",
  midpoint = 1,
  space = "Lab"
  ) + labs(fill="odds ratio")  + labs(fill="odds ratio")  + labs(title="stunting odds ratio", subtitle="controlling for maternal autonomy measures")

r4_g2<- ggplot(r4_geo) + geom_sf(aes(geometry=geometry, fill=Pr...t..), stat="sf")+ scale_fill_gradient2(low = "darkred" ,
  high ="#FFFF99", mid="white", midpoint= 0.05,
  ) + labs(fill="odds ratio")  + labs(fill="p-value")  + labs(title="stunting p-value", subtitle="controlling for maternal autonomy measures")

grid.arrange(r4_g1,r4_g2 , nrow=1)


```

model 6 

Controlling for all possible risk factors

```{r}

modeldistricts5<- svyglm(stunting ~ relevel(districts, ref='584') + caste_religion +  gender+ wealth+ ur+ fuel_type+ source_drinking +toilet_facility+ eb+ exc_b +vitA + immune + oral_rehyd + postnatal+ diarrhea+ inst_delivery+ 
             birth_size +low_birth_wt + zinc_d  + sev_anemia + son_pref +  od + no_ed + low_bmi + ba18 + anc+ iron_sup + mass_media,  syd,  family=binomial(link="logit"))

ci<- confint(modeldistricts5, level=0.95)

ci_l<- ci[, 1] %>% exp()
ci_u <- ci[, 2] %>% exp()

r5<- data.frame(summary(modeldistricts5)$coefficient)

r5<- tibble::rownames_to_column(r5, "coefficients")

r5<- r5 %>% mutate(ci_l= ci_l) %>% mutate(ci_u = ci_u)

r5 <- r5%>% filter(str_length(coefficients) == 34 ) 

r5$coefficients <- substr(r5$coefficients, 32, 34)

r5<- r5[-30:-31, ]

r5 <- r5 %>% mutate(odds_ratio = exp(Estimate)) %>% mutate(districts= k_districts)

r5
```

bar chart

```{r}
ggplot(r5) + geom_bar(aes(x= reorder(districts, odds_ratio), y=odds_ratio), fill="#009900", stat="identity") + 
  geom_errorbar(aes(x=reorder(districts, odds_ratio) , ymin=ci_l, ymax=ci_u)) + xlab("districts") + ylab("odds ratio")+ 
 labs(title= "stunting odds ratios across districts", subtitle="controlling for socioeconomic factors") +
  coord_flip()
```

```{r}

r5_geo<- merge(r5, geo, by.x="coefficients", by.y="REGCODE")

r5_g1<- ggplot(r5_geo) + geom_sf(aes(geometry=geometry, fill=Estimate), stat="sf")+ scale_fill_gradient2(low ="#FF9999",
  mid = "white",
  high = "darkred",
  midpoint = 1,
  space = "Lab"
  ) + labs(fill="odds ratio")  + labs(fill="odds ratio")  + labs(title="stunting odds ratio", subtitle="controlling for all risk factors")

r5_g2<- ggplot(r5_geo) + geom_sf(aes(geometry=geometry, fill=Pr...t..), stat="sf")+ scale_fill_gradient2(low = "darkred" ,
  high ="#FFFF99", mid="white", midpoint= 0.05,
  ) + labs(fill="p-value") 

grid.arrange(r5_g1,r5_g2 , nrow=1)

```


```{r}

```
